---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# packageC

<!-- badges: start -->
[![R-CMD-check](https://github.com/jstatlab/packageC/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jstatlab/packageC/actions/workflows/R-CMD-check.yaml)
![GitHub repo size](https://img.shields.io/github/repo-size/jstatlab/packageC)
![GitHub repo file count (file type)](https://img.shields.io/github/directory-file-count/jstatlab/packageC)
![Codecov](https://img.shields.io/codecov/c/github/jstatlab/packageC)
![GitHub R package version (subdirectory of monorepo)](https://img.shields.io/github/r-package/v/jstatlab/packageC)
![GitHub top language](https://img.shields.io/github/languages/top/jstatlab/packageC)
![GitHub License](https://img.shields.io/github/license/jstatlab/packageC)

<!-- badges: end -->

The goal of packageC is to make a minimal example using C code in R package.

## Installation

You can install the development version of packageC from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jstatlab/packageC")
```

## Example

Follow a basic example:

```{r example}
library(packageC)

y <- cumsum(rnorm(1e5))

plot(y, col = "grey")
lines(exp_smooth(y, 0.8), col = 2)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.
